Constrained, yet diverse: Phylogenetic and morphological filtering in epiphytic ferns

### 2019-08-08 ms/manuscript.Rmd
Don't show frond with in CWM figure
Use pdf instead of tiff for figs, fix indenting of authors

<!-- Set indent to about 3 characters throughout -->
\setlength{\parindent}{3ex}

@@

@@

**\fig \@ref(fig:cwm-div)**: Change in community-weighted mean (CWM) values of epiphytic and terrestrial fern communities along an elevational gradient on Moorea, French Polynesia. Epiphytic communities in green, terrestrial communities in brown. Error bars are community-weighted standard deviation (values below zero not shown). Trendlines and \rval^2^ shown for significant relationships with elevation or the interaction of elevation and growth habit as determined by a linear model at $\pval<0.05$. \tval shown for significant differences between means of CWMs by growth habit as determined by a two-sided \tval-test at $\pval<0.05$; $*** = \pval<0.001$; $** = \pval<0.01$; $* = \pval<0.05$.

@@

```{r traits-used-image, fig.width=7, fig.height=7, fig.cap = "Examples of traits used in this study."}
knitr::include_graphics(here::here("images/Figure_3_1_traits_lowres.pdf"))
```

@@

```{r climate, fig.height = 4, fig.width = 6, fig.cap = "Microclimatic variables."}
climate_plot
ggsave(plot = climate_plot, filename = here::here("ms/fig1.tiff"), height = 4, width = 6, units = "in", dpi = "retina")
```

@@

```{r pca, fig.height = 6, fig.width = 6, fig.cap = "Trait PCA."}
pca_plot
ggsave(plot = pca_plot, filename = here::here("ms/fig2.tiff"), height = 6, width = 6, units = "in", dpi = "retina")
```

@@

```{r tree, fig.height = 8, fig.width = 6, fig.cap = "Traits on tree."}
traits_with_tree
ggsave(plot = traits_with_tree, filename = here::here("ms/fig3.tiff"), height = 8, width = 6, units = "in", dpi = "retina")
```

@@

```{r heatmap, fig.height = 4, fig.width = 6, fig.cap = "Variable importance scores."}
importance_heatmap
ggsave(plot = importance_heatmap, filename = here::here("ms/fig4.tiff"), height = 4, width = 6, units = "in", dpi = "retina")
```

@@

```{r cwm-div, fig.height = 4, fig.width = 8, fig.cap = "Community-weighted means."}
combined_cwm_plots
ggsave(plot = combined_cwm_plots, filename = here::here("ms/fig5.tiff"), height = 4, width = 8, units = "in", dpi = "retina")
```

@@

```{r comm-div, fig.height = 8, fig.width = 4, fig.cap = "Community diversity metrics."}
combined_comm_div_plots
ggsave(plot = combined_comm_div_plots, filename = here::here("ms/fig6.tiff"), height = 8, width = 4, units = "in", dpi = "retina")
```

>>>>

<!-- Don't indent authors -->
\setlength{\parindent}{0ex}

@@

<!-- Set indent to about 3 characters hereafter -->
\setlength{\parindent}{3ex}

@@

**\fig \@ref(fig:cwm-div)**: Change in community-weighted mean (CWM) values of epiphytic and terrestrial fern communities along an elevational gradient on Moorea, French Polynesia. Epiphytic communities in green, terrestrial communities in brown. Error bars are each one standard deviation (values below zero not shown). Trendlines and \rval^2^ shown for significant relationships with elevation or the interaction of elevation and growth habit as determined by a linear model at $\pval<0.05$. \tval shown for significant differences between means of CWMs by growth habit as determined by a two-sided \tval-test at $\pval<0.05$; $*** = \pval<0.001$; $** = \pval<0.01$; $* = \pval<0.05$. Results for frond width were very similar to frond length and not shown.

@@

```{r traits-used-image, fig.height = 7, fig.width = 7, fig.cap = "Examples of traits used in this study."}
knitr::include_graphics(here::here("images/Figure_3_1_traits_lowres.pdf"))
```

@@

```{r climate, fig.height = 4, fig.width = 7, fig.cap = "Microclimatic variables."}
climate_plot
ggsave(plot = climate_plot, filename = here::here("ms/fig1.pdf"), height = 4, width = 7, units = "in")
```

@@

```{r pca, fig.height = 6, fig.width = 6, fig.cap = "Trait PCA."}
pca_plot
ggsave(plot = pca_plot, filename = here::here("ms/fig2.pdf"), height = 6, width = 6, units = "in")
```

@@

```{r tree, fig.height = 8, fig.width = 6, fig.cap = "Traits on tree."}
traits_with_tree
ggsave(plot = traits_with_tree, filename = here::here("ms/fig3.pdf"), height = 8, width = 6, units = "in")
```

@@

```{r heatmap, fig.height = 4, fig.width = 6, fig.cap = "Variable importance scores."}
importance_heatmap
ggsave(plot = importance_heatmap, filename = here::here("ms/fig4.pdf"), height = 4, width = 6, units = "in")
```

@@

```{r cwm-div, fig.height = 4, fig.width = 7, fig.cap = "Community-weighted means."}
combined_cwm_plots
ggsave(plot = combined_cwm_plots, filename = here::here("ms/fig5.pdf"), height = 4, width = 7, units = "in")
```

@@

```{r comm-div, fig.height = 8, fig.width = 4, fig.cap = "Community diversity metrics."}
combined_comm_div_plots
ggsave(plot = combined_comm_div_plots, filename = here::here("ms/fig6.pdf"), height = 8, width = 4, units = "in")
```
